\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{fontawesome5}
\usepackage{multicol}
\setlength{\multicolsep}{-3.0pt}
\setlength{\columnsep}{-1pt}
\input{glyphtounicode}


%----------FONT OPTIONS----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}

% serif
% \usepackage{CormorantGaramond}
% \usepackage{charter}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.7in}
\addtolength{\textheight}{1.4in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\classesList}[4]{
    \item\small{
        {#1 #2 #3 #4 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & \small #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{1.001\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & \small #2\\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemi{$\vcenter{\hbox{\tiny$\bullet$}}$}
\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.0in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

\def\CC{{C\nolinebreak[4]\hspace{-.05em}\raisebox{.4ex}{\tiny\bf ++}}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}


\begin{center}
    {\Huge \scshape Michael \underline{Hoon} Yong Hau} \\ \vspace{8pt}
    \small \raisebox{-0.1\height}\faPhone\ +65 97769494 $\vert$ \hspace*{0.1pt} \href{mailto:michael_hoon@mymail.sutd.edu.sg}{\raisebox{-0.2\height}\faEnvelope\  \underline{michael\_hoon@mymail.sutd.edu.sg}} \hspace*{0.1pt} $\vert$ \hspace*{0.1pt} 
    \href{https://linkedin.com/in/michaelhoon}{\raisebox{-0.2\height}\faLinkedin\ \underline{linkedin.com/in/michaelhoon}} \hspace*{0.1pt} $\vert$ \hspace*{0.1pt}
    \href{https://github.com/michael-hoon}{\raisebox{-0.2\height}\faGithub\ \underline{github.com/michael-hoon}}
\end{center}

\vspace{-15pt}

%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Singapore University of Technology and Design}{May 2026 -- Dec. 2026}
      {Master of Engineering (Research), Artificial Intelligence}{(Expected)}
    \resumeSubheading
      {Singapore University of Technology and Design}{Sep. 2022 -- May 2026}
      {Bachelor of Engineering, Engineering Systems and Design, Business Analytics Specialisation}{GPA: 4.59/5.0}
    \resumeSubheading
    {University of California, Berkeley}{Jun. 2023 -- Aug. 2023}
    {Summer Exchange, Econometrics}{Berkeley, CA}
  \resumeSubHeadingListEnd
% \vspace{-15pt}


%-----------EXPERIENCE-----------
\section{Experience}
% \vspace{-5pt}
  \resumeSubHeadingListStart
    \resumeSubheading
      {AI Engineer Intern}{Apr. 2024 -- Dec. 2024}
      {DSO National Laboratories}{Singapore}
      \resumeItemListStart
        \resumeItem{Deployed Retrieval Augmented Generation (RAG) pipeline for internal research assistant LLM application with open-sourced tools, significantly reducing man-hours required for staff to conduct research \& policy analysis.}
        \resumeItem{Implemented Advanced Agentic RAG techniques with Neo4j Knowledge Graph retrieval and Plan-and-Solve prompt engineering, significantly improving reasoning \& generation capabilities compared to vanilla RAG pipelines.} 
        \resumeItem{Optimised data pre-processing, generation, and retrieval pipelines through a comprehensive literature review of state of the art RAG techniques, to improve retrieval relevancy and ensure quality generated answers.} 
        \resumeItem{Participated in deploying the model within the company's local IT platforms, ensuring scalability and performance.}
      \resumeItemListEnd

    \resumeSubheading
      {Data Analyst Intern}{Jan. 2024 -- Apr. 2024}
      {Poh Tiong Choon Logistics Ltd.}{Singapore}
      \resumeItemListStart
        \resumeItem{Worked on Supply Chain Analytics, analysing cross-department delivery driver dataset to derive insights and optimize business strategies. Identified key areas for improvement in scheduling and boosted driver utilisation rates by 20\%.}
        \resumeItem{Developed end-to-end automated data pipeline solution for cleaning and analysis with bash scripts, integrating existing database system with Python, significantly reducing working man-hours.} 
        \resumeItem{Created PowerBI Dashboard for key metrics and patterns on route analysis. Wrote internal report discussing findings}
      \resumeItemListEnd

    \resumeSubheading
      {Data Analyst Intern}{Sep. 2022 -- Jan. 2023}
      {Aviation Studies Institute, SUTD}{Singapore}
      \resumeItemListStart
        \resumeItem{Extracted key business insights for industry partner, International Air Transport Association (IATA), via Exploratory Data Analysis in R, SQL, and Python. Conducted economic analysis of air cargo demand in Southeast Asia.}
        \resumeItem{Developed correlation models for predictive analysis of internal air cargo demand data with open-sourced economic data. Evaluated hypothesis on key drivers of regional air cargo demand.}
        \resumeItem{Wrote an internal paper discussing findings, presented to IATA and the Civil Aviation Authority of Singapore.}
      \resumeItemListEnd

  %   \resumeSubheading
  %     {Undergraduate Research Assistant}{Oct. 2022 -- Dec. 2023}
  %     {Singapore University of Technology and Design}{Singapore}
  %     \resumeItemListStart
  %       \resumeItem{Explored computational modelling of materials via the Particle-In-Cell (PIC) and Finite-Difference-Time-Domain (FDTD) methods, and conducted qualitative analysis on resulting spectra.}
  %       \resumeItem{Research showed similar scattering patterns and Lorentzian behaviour, and will contribute to further studies in simulating optoelectronic devices.}
  %       \resumeItem{Worked with open-source code developed in Python using the MEEP library, and PIC algorithm developed via Epoch.}
  %   \resumeItemListEnd
  \resumeSubHeadingListEnd
    % \resumeSubheading
    %   {Research Intern}{Mar. 2018 -- Apr. 2019}
    %   {Satellite Research Centre (SaRC), Nanyang Technological University}{Singapore}
    %   \resumeItemListStart
    %     \resumeItem{Worked on SCOOB-I, a student-built satellite, with main mission to detect and characterise the electromagnetic spectral emissions of the Sun and Earth in the Near-Infrared, Visible, and Ultraviolet spectrum ranges.}
    %     \resumeItem{Designed the Electrical Interfacing architecture of SCOOB-I's subsystems and its numerous research payloads, and explored hardware considerations for a 3U CubeSat in Low-Earth Orbit.}
    %     \resumeItem{SCOOB-I was launched by ISRO's PSLV C-53 mission on 30th June 2022, and is Singapore’s first Heliophysics mission.}
    % \resumeItemListEnd
% \vspace{-20pt}

% \vspace{-10pt}
%-----------PROJECTS-----------
\section{Projects}
    \vspace{-5pt}
    \resumeSubHeadingListStart
      \resumeProjectHeading
          {\textbf{LepakLah!} $|$ \emph{Python, FastAPI, MySQL, Docker, Kubernetes, Flutter}}{Aug. 2024 -- Sep. 2024}
          \resumeItemListStart
            \resumeItem{Developed a Flutter-based mobile application as part of Dell InnovateFest, a Public-Good hackathon to combat social isolation among the Elderly. Represented University and \textbf{won 3rd place award.}}
            \resumeItem{Integrated a generative AI model (LLM) to produce personalized workshop ideas based on existing data, and an image-generation model to create visual samples of activities. Models deployed on NVIDIA NIM platform.}
            \resumeItem{Developed System Architecture, containerised application backend with Docker and managed with Kubernetes, ensuring scalability and efficiency on a cloud-native environment. Deployed on Red Hat OpenShift platform.}
          \resumeItemListEnd
    \vspace{-12pt}
      \resumeProjectHeading
          {\textbf{CareerQuest} $|$ \emph{React.js, Vite.js, Tailwind CSS, Firebase}}{Aug. 2024 -- Sep. 2024}
          \resumeItemListStart
            \resumeItem{Built a full stack responsive web application as part of the Open Goverment Products Build for Good 2024 hackathon, a platform that supports Education and Career Guidance for Junior College students.}
            % \resumeItem{Incorporated a generative AI (LLM) model for career and industry suggestions based on user profile and interests, using OpenAI's API and effective prompt engineering techniques.}
            \resumeItem{Used React.js + Vite.js and Tailwind CSS for the frontend UI, with Firebase as the backend server, deployed application on Firebase Cloud. Ensured proper CI/CD practices using GitHub workflows.}
            \resumeItem{Conducted proper user research, user testing, and stakeholder analysis with relevant government statutory boards, and incorporated the entire product design workflow in designing the solution.}
          \resumeItemListEnd
    \vspace{-12pt}
    \newpage
      \resumeProjectHeading
          {\textbf{Transportation Analytics} $|$ \emph{R, Discrete Choice Modelling, Econometrics}}{Aug. 2024 -- Aug. 2024}
          \resumeItemListStart
            \resumeItem{Internal Kaggle Competition on transportation analytics with General Motors dataset, to predict consumer choices among bundles of safety features in cars using Discrete Choice Models.}
            \resumeItem{Developed and tested multiple models in \emph{R} such as Multinomial Logit, Mixed Logit, Random Forest, and XGBoost, validating model results on a private test set using a cross-entropy loss metric.}
            \resumeItem{Fine-tuned model with hyperparameter grid search and introduced stacking techniques such as Meta-Learning to implement a soft-voting classifier, obtaining \textbf{2nd place overall}. Discussed model interpretability with SHAP values.}
          \resumeItemListEnd
    \vspace{-12pt}
      \resumeProjectHeading
          {\textbf{MRP Backend System} $|$ \emph{Python, SQL, Docker, Microsoft Azure, Airflow}}{Jun. 2024 -- Aug. 2024}
          \resumeItemListStart
            \resumeItem{Designed and implemented a backend system for Materials Requirement Planning (MRP) for a supply chain project, optimizing inventory management by forecasting material requirements and automating workflows.}
            \resumeItem{Developed an end-to-end ETL pipeline with Python, SQL, Azure Cloud Platform, and orchestrated automated DAG workflows with Apache Airflow. Back-end microservices containerised with Docker, validated data with Pydantic.}
            \resumeItem{Integrated system with SQL database to store and retrieve data on Microsoft Azure Cloud Platform, enabling a scalable, secure, and reliable cloud-based data storage.}
          \resumeItemListEnd
      % \resumeProjectHeading
      %     {\textbf{FinSight.AI} $|$ \emph{Python, LangChain, Streamlit}}{Mar. 2024 -- Mar. 2024}
      %     \resumeItemListStart
      %       \resumeItem{Industry hackathon with Temasek Holdings (Financial Services Department): Large Language Model (LLM) enabled Financial Analysis Assistant via RAG, scalable with existing in-house data infrastructure.}
      %       \resumeItem{Summarizes multiple unstructured financial reports and key metrics with internal data, reducing man-hours by 80\%. Able to retrieve metadata of reports and allow user to self-verify sources, and provide semantic score results.}
      %     \resumeItemListEnd
          % \vspace{-5pt}
    \resumeSubHeadingListEnd

    % \resumeSubHeadingListStart
    %   \resumeProjectHeading
    %       {\textbf{LangChain PDF Querying Assistant} $|$ \emph{Python, LangChain, Streamlit, Docker}}{Sep. 2023 -- Nov. 2023}
    %       \resumeItemListStart
    %         \resumeItem{Developed a Querying System Chatbot via LangChain, for Question-Answering (QA) over PDFs.}
    %         \resumeItem{Feasible use cases include summarisation of large PDF articles in academia, and document management systems.}
    %         \resumeItem{Application hosted and deployed on Streamlit webapp, containerised using Docker.}
    %       \resumeItemListEnd
    %       % \vspace{-13pt}
    % \resumeSubHeadingListEnd

% \newpage

% ------RELEVANT COURSEWORK-------
\section{Relevant Coursework}
    % \resumeSubHeadingListStart
        \begin{multicols}{3}
            \begin{itemize}[itemsep=-5pt, parsep=3pt]
                \item\small Applied Machine Learning  
                \item Optimisation
                \item Natural Language Processing
                \item Statistics \& Econometrics 
                \item Data Science
                \item Data Engineering
            \end{itemize}
        \end{multicols}
        % \vspace*{2.0\multicolsep}
    % \resumeSubHeadingListEnd

%-----------PROGRAMMING SKILLS-----------
\section{Skills}
  \begin{itemize}[leftmargin=0.15in, label={}]
      \small{\item{
      \textbf{Languages}{: Python, R, SQL, Julia, \LaTeX} \\
      \textbf{Tools}{: Git, Docker, Kubernetes, Linux/Bash, Ollama, Neo4j, Microsoft Azure, Firebase, Apache Airflow} \\
      \textbf{Libraries/Frameworks}{: LangChain, HuggingFace, PyTorch, Pandas, NumPy, scikit-learn, FastAPI, tidyverse (R)}  \\
      }}
  \end{itemize} 
% \vspace{-18pt}

%-----------INVOLVEMENT---------------
% \section{Extracurricular}
%     \resumeSubHeadingListStart
%         \resumeSubheading{SUTD Organisation of Autonomous Robotics}{Mar. 2023 -- Feb. 2024}{Secretary}{Singapore University of Technology and Design}
%             \resumeItemListStart
%                 \resumeItem{Organised a school-wide robotics competition (RoboClash 2024), attracting over 80 participants and 15 teams.}
%                 \resumeItem{Collaborated with school administration on all administrative matters related to the club, conducted school-wide workshops to inspire robotics technology among students.}
% %                \resumeItem{Spearheaded and led a new robotics research project, working on Multi-Agent Reinforcement Learning.}
%             \resumeItemListEnd
%     \resumeSubHeadingListEnd
% \vspace{-18pt}

\end{document}
