\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{fontawesome5}
\usepackage{multicol}
\setlength{\multicolsep}{-3.0pt}
\setlength{\columnsep}{-1pt}
\input{glyphtounicode}


%----------FONT OPTIONS----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}

% serif
% \usepackage{CormorantGaramond}
% \usepackage{charter}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\classesList}[4]{
    \item\small{
        {#1 #2 #3 #4 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & \small #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{1.001\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & \small #2\\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemi{$\vcenter{\hbox{\tiny$\bullet$}}$}
\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.0in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

\def\CC{{C\nolinebreak[4]\hspace{-.05em}\raisebox{.4ex}{\tiny\bf ++}}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}


\begin{center}
    {\Huge \scshape Michael \underline{Hoon} Yong Hau} \\ \vspace{8pt}
    \small \raisebox{-0.1\height}\faPhone\ +65 97769494 ~ \href{mailto:michael_hoon@mymail.sutd.edu.sg}{\raisebox{-0.2\height}\faEnvelope\  \underline{michael\_hoon@mymail.sutd.edu.sg}} ~ 
    \href{https://linkedin.com/in/michaelhoon}{\raisebox{-0.2\height}\faLinkedin\ \underline{linkedin.com/in/michaelhoon}}  ~
    \href{https://github.com/michael-hoon}{\raisebox{-0.2\height}\faGithub\ \underline{github.com/michael-hoon}}
    % \vspace{-8pt}
\end{center}


%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Singapore University of Technology and Design}{May 2026 -- Dec. 2026}
      {Master of Engineering (Research)}{(Expected)}
    \resumeSubheading
      {Singapore University of Technology and Design}{Sep. 2022 -- May 2026}
      {Bachelor of Engineering, Engineering Systems and Design, Minor in Computer Science}{Current GPA: 4.83/5.0}
    \resumeSubheading
    {University of California, Berkeley}{Jun. 2023 -- Aug. 2023}
    {Summer Exchange}{Berkeley, CA}
  \resumeSubHeadingListEnd
% \vspace{-15pt}

%------RELEVANT COURSEWORK-------
\section{Coursework / Certifications}
    %\resumeSubHeadingListStart
        \begin{multicols}{3}
            \begin{itemize}[itemsep=-5pt, parsep=3pt]
                \item\small Machine Learning  
                \item Deep Learning
                \item Natural Language Processing
                \item Applied Econometrics
                \item Data Science / Business Analytics 
                \item Mathematical Modelling
            \end{itemize}
        \end{multicols}
        % \vspace*{2.0\multicolsep}
    %\resumeSubHeadingListEnd

%
%-----------PROGRAMMING SKILLS-----------
\section{Skills}
  \begin{itemize}[leftmargin=0.15in, label={}]
      \small{\item{
      \textbf{Languages}{: Python, R, SQL, Julia, \LaTeX} \\
      \textbf{Tools}{: Git/GitHub, Docker, Streamlit, DBeaver, VS Code, Vim} \\
      \textbf{Libraries/Frameworks}{: LangChain, Pandas, NumPy, Plotly, OpenAI API, tidyverse (R)}  \\
      }}
  \end{itemize} 
% \vspace{-18pt}

%-----------PROJECTS-----------
\section{Projects}
    % \vspace{-5pt}
    
    \resumeSubHeadingListStart
      \resumeProjectHeading
          {\textbf{RAG-Based LLM Applications} $|$ \emph{Python, LangChain}}{Dec. 2023 -- Present}
          \resumeItemListStart
            \resumeItem{Currently experimenting with Retrieval Augmented Generation (RAG) applications with open-source Large Language Models (LLMs).}
            \resumeItem{Exploring inference with open-source LLMs, model Fine-Tuning with Amazon Sagemaker Jumpstart, and model testing \& evaluation via LangSmith.}
          \resumeItemListEnd
          \vspace{-13pt}
    \resumeSubHeadingListEnd

    \resumeSubHeadingListStart
      \resumeProjectHeading
          {\textbf{LangChain PDF Querying System} $|$ \emph{Python, LangChain, Streamlit, Docker}}{Sep. 2023 -- Nov. 2023}
          \resumeItemListStart
            \resumeItem{Developed a Querying System Chatbot via LangChain, for Question-Answering (QA) over PDFs.}
            \resumeItem{Feasible use cases include summarisation of large PDF articles in academia, and document management systems.}
            \resumeItem{Application hosted and deployed on Streamlit webapp, containerised using Docker.}
          \resumeItemListEnd
          % \vspace{-13pt}
    \resumeSubHeadingListEnd

%-----------EXPERIENCE-----------
\section{Experience}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Undergraduate Research Assistant}{Sep. 2022 -- Jan. 2023}
      {Aviation Studies Institute}{Singapore}
      \resumeItemListStart
        \resumeItem{Extracted key business insights for industry partner, International Air Transport Association (IATA), via Exploratory Data Analysis in R, SQL, and Python. Visualised data via Plotly and R.}
        \resumeItem{Developed correlation models for predictive analysis of internal air cargo demand data.}
        \resumeItem{Wrote an internal paper discussing findings, and presented to IATA and the Civil Aviation Authority of Singapore.}
      \resumeItemListEnd

    \resumeSubheading
      {Undergraduate Research Assistant}{Oct. 2022 -- Dec. 2023}
      {Singapore University of Technology and Design}{Singapore}
      \resumeItemListStart
        \resumeItem{Explored computational modelling of materials via the Particle-In-Cell (PIC) and Finite-Difference-Time-Domain (FDTD) methods, and conducted qualitative analysis on resulting spectra.}
        \resumeItem{Research showed similar scattering patterns and Lorentzian behaviour, and will contribute to further studies in simulating optoelectronic devices.}
        \resumeItem{Worked with open-source code developed in Python using the MEEP library, and PIC algorithm developed via Epoch.}
    \resumeItemListEnd

    % \resumeSubheading
    %   {Research Intern}{Mar. 2018 -- Apr. 2019}
    %   {Satellite Research Centre (SaRC), Nanyang Technological University}{Singapore}
    %   \resumeItemListStart
    %     \resumeItem{Worked on SCOOB-I, a student-built satellite, with main mission to detect and characterise the electromagnetic spectral emissions of the Sun and Earth in the Near-Infrared, Visible, and Ultraviolet spectrum ranges.}
    %     \resumeItem{Designed the Electrical Interfacing architecture of SCOOB-I's subsystems and its numerous research payloads, and explored hardware considerations for a 3U CubeSat in Low-Earth Orbit.}
    %     \resumeItem{SCOOB-I was launched by ISRO's PSLV C-53 mission on 30th June 2022, and is Singapore’s first Heliophysics mission.}
    % \resumeItemListEnd
    
  \resumeSubHeadingListEnd
% \vspace{-20pt}



%-----------INVOLVEMENT---------------
\section{Extracurricular}
    \resumeSubHeadingListStart
        \resumeSubheading{SUTD Organisation of Autonomous Robotics}{Mar. 2023 -- Feb. 2024}{Secretary}{Singapore University of Technology and Design}
            \resumeItemListStart
                \resumeItem{Organised a school-wide robotics competition (RoboClash 2024), attracting over 80 participants and 15 teams.}
                \resumeItem{Collaborated with school administration on all administrative matters related to the club, conducted school-wide workshops to inspire robotics technology among students.}
%                \resumeItem{Spearheaded and led a new robotics research project, working on Multi-Agent Reinforcement Learning.}
            \resumeItemListEnd
    \resumeSubHeadingListEnd
% \vspace{-18pt}



\end{document}
