\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{fontawesome5}
\usepackage{multicol}
\setlength{\multicolsep}{-3.0pt}
\setlength{\columnsep}{-1pt}
\input{glyphtounicode}


%----------FONT OPTIONS----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}

% serif
% \usepackage{CormorantGaramond}
% \usepackage{charter}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.7in}
\addtolength{\textheight}{1.4in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\classesList}[4]{
    \item\small{
        {#1 #2 #3 #4 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & \small #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{1.001\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & \small #2\\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemi{$\vcenter{\hbox{\tiny$\bullet$}}$}
\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.0in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

\def\CC{{C\nolinebreak[4]\hspace{-.05em}\raisebox{.4ex}{\tiny\bf ++}}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}


\begin{center}
    {\Huge \scshape Michael \underline{Hoon} Yong Hau} \\ \vspace{8pt}
    \small \raisebox{-0.1\height}\faPhone\ +65 97769494 $\vert$ \hspace*{0.1pt} \href{mailto:michael_hoon@mymail.sutd.edu.sg}{\raisebox{-0.2\height}\faEnvelope\  \underline{michael\_hoon@mymail.sutd.edu.sg}} \hspace*{0.1pt} $\vert$ \hspace*{0.1pt} 
    \href{https://linkedin.com/in/michaelhoon}{\raisebox{-0.2\height}\faLinkedin\ \underline{linkedin.com/in/michaelhoon}} \hspace*{0.1pt} $\vert$ \hspace*{0.1pt}
    \href{https://github.com/michael-hoon}{\raisebox{-0.2\height}\faGithub\ \underline{github.com/michael-hoon}}
\end{center}

\vspace{-15pt}

%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Singapore University of Technology and Design}{Sep. 2022 -- May 2026}
      {Bachelor of Engineering, Engineering Systems and Design, Business Analytics Specialisation}{Singapore}
    \resumeSubheading
    {University of California, Berkeley}{Jun. 2023 -- Aug. 2023}
    {Summer Exchange, Econometrics}{Berkeley, CA}
  \resumeSubHeadingListEnd
% \vspace{-15pt}


%-----------EXPERIENCE-----------
\section{Experience}
% \vspace{-5pt}
  \resumeSubHeadingListStart
    \resumeSubheading
      {AI Engineer Intern}{Apr. 2024 -- Dec. 2024}
      {DSO National Laboratories}{Singapore}
      \resumeItemListStart
        \resumeItem{Deployed a full-stack, fully local Retrieval Augmented Generation (RAG) pipeline as internal AI research assistant, significantly reducing man-hours required for staff to conduct research \& policy analysis.}
        \resumeItem{Conducted extensive literature review on state-of-the-art RAG techniques, and implemented the GraphReader paper LLM agent for on-premise deployment with Streamlit frontend.}
        \resumeItem{Implemented a Multi-Agent RAG approach with a Neo4j Knowledge Graph database for agentic retrieval strategy, significantly improving reasoning \& generation capabilities compared to vanilla RAG pipelines.} 
      \resumeItemListEnd

    \resumeSubheading
      {Data Analyst Intern}{Jan. 2024 -- Apr. 2024}
      {Poh Tiong Choon Logistics Ltd.}{Singapore}
      \resumeItemListStart
        \resumeItem{Worked on Supply Chain Analytics, analysing cross-department delivery driver dataset to derive insights and optimize business strategies. Identified key areas for improvement in scheduling and boosted driver utilisation rates by 20\%.}
        \resumeItem{Developed end-to-end automated data pipeline solution for cleaning and analysis with bash scripts, integrating existing database system with Python, significantly reducing working man-hours.} 
        \resumeItem{Created PowerBI Dashboard for key metrics and patterns on route analysis. Wrote internal report discussing findings}
      \resumeItemListEnd
  \resumeSubHeadingListEnd

%-----------PROJECTS-----------
\section{Projects}
    \vspace{-5pt}
    \resumeSubHeadingListStart
      \resumeProjectHeading
          {\textbf{LepakLah!} $|$ \emph{Python, FastAPI, MySQL, Docker, Kubernetes, Flutter}}{Aug. 2024 -- Sep. 2024}
          \resumeItemListStart
            \resumeItem{Developed a Flutter-based mobile application as part of Dell InnovateFest, a Public-Good hackathon to combat social isolation among the Elderly. Represented University and \textbf{won 3rd place award.}}
            \resumeItem{Integrated a generative AI model (LLM) to produce personalized workshop ideas based on existing data, and an image-generation model to create visual samples of activities. Models deployed on NVIDIA NIM platform.}
            \resumeItem{Developed System Architecture, containerised application backend with Docker and managed with Kubernetes, ensuring scalability and efficiency on a cloud-native environment. Deployed on Red Hat OpenShift platform.}
          \resumeItemListEnd
    \vspace{-12pt}
      \resumeProjectHeading
          {\textbf{Transportation Analytics} $|$ \emph{R, Discrete Choice Modelling, Econometrics}}{Aug. 2024 -- Aug. 2024}
          \resumeItemListStart
            \resumeItem{Internal Kaggle Competition on transportation analytics with General Motors dataset, to predict consumer choices among bundles of safety features in cars using Discrete Choice Models.}
            \resumeItem{Developed and tested multiple models in \emph{R} such as Multinomial Logit, Mixed Logit, Random Forest, and XGBoost, validating model results on a private test set using a cross-entropy loss metric.}
            \resumeItem{Fine-tuned model with hyperparameter grid search and introduced stacking techniques such as Meta-Learning to implement a soft-voting classifier, obtaining \textbf{2nd place overall}. Discussed model interpretability with SHAP values.}
          \resumeItemListEnd
    \vspace{-12pt}
      \resumeProjectHeading
          {\textbf{MRP Backend System} $|$ \emph{Python, SQL, Docker, Microsoft Azure, Apache Airflow}}{Jun. 2024 -- Aug. 2024}
          \resumeItemListStart
            \resumeItem{Designed and implemented a backend system for Materials Requirement Planning (MRP) for a supply chain project, optimizing inventory management by forecasting material requirements and automating workflows.}
            \resumeItem{Developed an end-to-end ETL pipeline with Python, SQL, Azure Cloud Platform, and orchestrated automated DAG workflows with Apache Airflow. Back-end microservices containerised with Docker, validated data with Pydantic.}
            \resumeItem{Integrated system with SQL database to store and retrieve data on Microsoft Azure Cloud Platform, enabling a scalable, secure, and reliable cloud-based data storage.}
          \resumeItemListEnd
    \resumeSubHeadingListEnd

%-----------PROGRAMMING SKILLS-----------
\section{Skills}
  \begin{itemize}[leftmargin=0.15in, label={}]
      \small{\item{
      \textbf{Languages}{: Python, R, SQL, Julia, \LaTeX} \\
      \textbf{Tools}{: Git, Docker, Kubernetes, Linux/Bash, Ollama, Neo4j, Microsoft Azure, Firebase, Apache Airflow} \\
      \textbf{Libraries/Frameworks}{: LangChain, HuggingFace, PyTorch, Pandas, NumPy, scikit-learn, FastAPI, tidyverse (R)}  \\
      }}
  \end{itemize} 

\end{document}
